\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students

### 2023-11-04 demystify.tex
updates

\subsection{How do I address a professor?}

@@

>>>>

\subsection{How do I address a professor?}\label{sec:address}

@@

\paragraph{Gifts and professionalism} In many countries, it's customary to give professors gifts, often during holidays.  These gifts can be costly and expected by professors. In the US, it's not a common practice, and it's perfectly acceptable not to give gifts. However, if you'd like to offer small souvenir-like tokens, it's a thoughtful gesture that's appreciated. Professors often display such gifts proudly, and they can come from students, colleagues, or when they travel. In summary, small gifts are fine, but avoid anything that might make your professors uncomfortable.

There appears to be a misconception that in the US things are strictly business-oriented, e.g., profs are your bosses who pay students for their work. And if you do something nice, then your action can be interpreted as you want something in return.  However, the reality is quite the opposite. While in the US people can be a bit more straightforward and direct (e.g., your prof. will let you know quickly if they don't like something), they are also friendly and informal.  For example, you can call your prof by their first name (\S\ref{sec:address}), you can disagree with them (and actually gain lots of respect doing so), you can ask them for help (even on personal issues---they might not be able to help, but they can listen and might have good advice), you can come to their house for parties, and of course you can even give them small thoughtful gifts that they put on their desks.  
Note that many students and professors have long lifetime relationships beyond the student's academic journey. For example, I still keep in touch with many of my mentors (even my 9th grade teacher in Hawaii), and friends through cards, emails, and phone calls during holidays or simply whenever I see something remind me of them.  These practices are genuine and serve as a meaningful way to stay connected with others.

% There is a common misconception that the United States maintains a strictly business-oriented and purely professional atmosphere, where professors are viewed as bosses who pay students for their work. However, the reality is quite the opposite. While it's true that Americans tend to be more straightforward and direct in their interactions, they also value friendliness and informality.

% For instance, in the United States, it's perfectly acceptable to address your professor by their first name (as discussed in Section \ref{sec:address}). Students can also express their disagreements with professors, and in doing so, they can actually earn a great deal of respect. Moreover, you can approach your professors for assistance, even on personal matters. While they might not always have the answers, they are often willing to listen and offer valuable advice.

% A unique aspect of the American academic culture is the opportunity for social interaction with professors. It's not uncommon for students to be invited to their professors' homes for parties and gatherings, such as Thanksgiving dinners, which can foster a sense of community and camaraderie.

% In addition, small, thoughtful gifts are often exchanged between students and professors, and it's heartwarming to see these tokens displayed on professors' desks, symbolizing the strong connections that can develop between them.

% What's particularly noteworthy is the enduring relationships that many students and professors maintain well beyond the student's academic journey. These connections can span a lifetime, with individuals staying in touch through cards, emails, and phone calls during holidays or simply when something reminds them of one another. This practice serves as a genuine and meaningful way to stay connected with mentors and friends, reflecting the deep-rooted value of maintaining relationships in American society.
